### 2024-03-03 presentation/parts/presentation_introduction.tex
WIP

    \note[item]{Machine learning for healthcare touches on most of these aspects. Fx:}
    \note[item]{
        \begin{itemize}
            \item \textbf{Prevention} by predicting risk of disease allowing for early intervention.
            \item \textbf{Diagnosis} by detecting stroke in emergency calls.
            \item \textbf{Treatment} by suggesting medication.
            \item Even \textbf{Cure} by helping to find new cures or treatments for diseases.
        \end{itemize}
    }
\end{frame}

\begin{frame}[t]
    \frametitle{Medical dialogue}
    \begin{columns}[t]
        \begin{column}{0.4\textwidth}
            Every interaction within a healthcare system is a form of \highlight{medical dialogue}:
            \begin{itemize}
                \item <1> General practitioner
                \item <1> Nurse
                \item <1> Midwife
                \item <1> Emergency medical dispatcher
                \item <1> Paramedic
                \item <1> Emergency room
                \item <1> Health insurance
            \end{itemize}
        \end{column}
        \begin{column}{0.6\textwidth}
            \vspace{-2em}
            \begin{figure}[t]
                \centering
                \includegraphics[width=0.9\textwidth]{figures/corti_sketch_conversations.png}
            \end{figure}
        \end{column}
    \end{columns}

@@

    \note[item]{Machine learning can help in many ways.}
    \note[item]{The main goal of augmenting communication is:
        \begin{itemize}
            \item Reduce the impact of medical errors and adverse events.
            \item Free up time spent on documentation for patient care.
        \end{itemize}
    }
\end{frame}

\begin{frame}
    \frametitle{Reliability of machine learning systems}
    \begin{itemize}
        \item <1-> \highlight{Data}: Quality, quantity, diversity, bias, privacy, ethics.
        \item <2-> \highlight{Task}: Context, domain, language, culture, purpose.
        \vspace{1em}
        \item <3-> \highlight{Interpretability} of how a model works (transparency, accountability, regulation).
        \item <4-> \highlight{Explainability} of model predictions (trust, understanding, feedback).
        \item <5-> \highlight{Fairness} in treatment of different groups of people.
        \item <6-> \highlight{Robustness} to noise, outliers, distribution shift, and adversarial attacks.
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Building a decision-support system}
    \begin{columns}
        \begin{column}{0.6\textwidth}
            Modular approach:
            \begin{itemize}
                \item <2-> \highlight{Source data}: Speech or text (potentially images, video, electronic health records, etc.).
                \item <3-> \highlight{Foundation modelling}: Converting the input into representations useful for downstream tasks.
                \item <4-> \highlight{Downstream tasks}: Suggesting, summarizing, classifying, transcribing, translating, etc.
                \item <5-> \highlight{Uncertainty}: Estimating the reliability of data, representations, predictions.
            \end{itemize}
        \end{column}
        \begin{column}{0.4\textwidth}
            \resizebox{0.8\textwidth}{!}{%
            \begin{tikzpicture}[x=1cm,y=1cm]
                \node [mybox, fill=white] at (0,5) (predictions_white) {};
                \node<4-> [mybox, fill=presentation_orange] at (0,5) (predictions) {};
                \foreach \i in {-11,...,11} {
                    \fill<4->[myrect, fill=presentation_orange_shaded] (0.2*\i,4.8) rectangle ++(0.1,0.4);
                }
                \node<4-> [] at (0,5) {\small\textsc{predictions}};

@@

                \node<5-> [draw, rectangle, rounded corners, line width=0.15cm, presentation_red, fit=(speech)(representation)(recognition)(text)(predictions), inner sep=10pt] (uncertainty) {};
                \node<5-> [above] at (uncertainty.north) {\small\textsc{uncertainty}};
            \end{tikzpicture}
        }
        \end{column}
    \end{columns}
\end{frame}

>>>>

    \note[item]{Machine learning for healthcare touches on most of these aspects. Fx:}
    \note[item]{
        \begin{itemize}
            \item \textbf{Prevention} by predicting risk of disease allowing for early intervention.
            \item \textbf{Diagnosis} by detecting stroke in emergency calls.
            \item \textbf{Treatment} by suggesting medication.
        \end{itemize}
    }
\end{frame}

\begin{frame}[t]
    \frametitle{Medical dialogue}
    \begin{columns}[t]
        \begin{column}{0.4\textwidth}
            Central to an \highlight{interaction} within a healthcare system is the \highlight{medical dialogue}:
            % Every interaction within a healthcare system is a form of \highlight{medical dialogue}:
            \begin{itemize}
                \item <1> General practitioner
                \item <1> Nurse
                \item <1> Midwife
                \item <1> Emergency medical dispatcher
                \item <1> Paramedic
                \item <1> Emergency room
                \item <1> Health insurance
            \end{itemize}
        \end{column}
        \begin{column}{0.6\textwidth}
            \vspace{-2em}
            \begin{figure}[t]
                \centering
                \includegraphics[width=0.9\textwidth]{figures/corti_sketch_conversations.png}
            \end{figure}
        \end{column}
    \end{columns}

@@

    \note[item]{Machine learning can help in many ways.}
    \note[item]{The main goal of augmenting communication is:
        \begin{itemize}
            \item Reduce the impact.
            \item Free up time.
        \end{itemize}
    }
\end{frame}

\begin{frame}
    \frametitle{Reliability of machine learning systems}
    \begin{itemize}
        \item <1-> \highlight{Data}: Quality, quantity, diversity, bias, privacy, ethics.
        \item <1-> \highlight{Task}: Context, domain, language, culture, purpose.
        \vspace{1em}
        \item <2-> \highlight{Interpretability} of how a model works (transparency, accountability, regulation).
        \item <2-> \highlight{Explainability} of model predictions (trust, understanding, feedback).
        \item <2-> \highlight{Fairness} in treatment of different groups of people.
        \item <2-> \highlight{Robustness} to noise, outliers, distribution shift, and adversarial attacks.
    \end{itemize}

    \note[item]{So what are the challenges holding us back in implementing such systems?}
    \note[item]{
        \begin{itemize}
            \item Strong requirements of data.
            \item Tasks that span different contexts, domains, languages, and cultures.
            \item Regulatory requirements for transparency and accountability.
            \item Trust and understanding of predictions.
        \end{itemize}
    }
\end{frame}

@@

\begin{frame}
    \frametitle{Building a decision-support system}
    \begin{columns}
        \begin{column}{0.6\textwidth}
            % Modular approach:
            \begin{itemize}
                \item <2-> \highlight{Source data}: Speech or text (potentially images, video, electronic health records, etc.).
                \item <3-> \highlight{Foundation modelling}: Converting the input into representations useful for downstream tasks.
                \item <4-> \highlight{Downstream tasks}: Suggesting, summarizing, classifying, transcribing, translating, etc.
                \item <5-> \highlight{Uncertainty}: Estimating the reliability of data, representations, predictions.
            \end{itemize}
        \end{column}
        \begin{column}{0.4\textwidth}
            \resizebox{0.8\textwidth}{!}{%
            \begin{tikzpicture}[x=1cm,y=1cm]
                \node [mybox, fill=white] at (0,5) (predictions_white) {};
                \node<4-> [mybox, fill=presentation_orange] at (0,5) (predictions) {};
                \foreach \i in {-11,...,11} {
                    \fill<4->[myrect, fill=presentation_orange_shaded] (0.2*\i,4.8) rectangle ++(0.1,0.4);
                }
                \node<4-> [] at (0,5) {\small\textsc{predictions}};

@@

                \node<5-> [draw, rectangle, rounded corners, line width=0.15cm, presentation_red, fit=(speech)(representation)(recognition)(text)(predictions), inner sep=10pt] (uncertainty) {};
                \node<5-> [above] at (uncertainty.north) {\small\textsc{uncertainty}};
            \end{tikzpicture}
        }
        \end{column}
    \end{columns}

    \note[item]{We will take a modular approach to building a decision-support system.}
    \note[item]{First we need source data}
    \note[item]{Then we need to convert it into representations useful for downstream tasks.}
    \note[item]{Then we can perform the downstream tasks.}
    \note[item]{Finally, we need to estimate the reliability of our data, representations, and predictions.}
\end{frame}
